How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-06 tse-paper/content.tex
describe results of literature survey

% Our study of the three techniques on \emph{LogChunks} shows that
% \begin{itemize}
%   \item PBE yields very accurate results when trained with two examples
%   from a
%   single structural category.
%   \item CTS shows the best average precision, though precision and
recall
%   of a
%   retrieval is hard to determine from the given result.
%   A small increase in the number of training examples has no noticeable
%   influence.

@@

The full data extraction template and our results of this step can be
found in our replication package~\cite{brandt2020chunk-replication}.

\subsection{Results}
lots of:
- categories + frequencies of answers

\subsubsection{Retrieved Information}

\subsubsection{Retrieval Technique}

\subsubsection{Build Logs}

>>>>

% Our study of the three techniques on \emph{LogChunks} shows that
% \begin{itemize}
%   \item PBE yields very accurate results when trained with two examples
%   from a
%   single structural category.
%   \item CTS shows the best average precision, though precision and
% recall
%   of a
%   retrieval is hard to determine from the given result.
%   A small increase in the number of training examples has no noticeable
%   influence.

@@

The full data extraction template and our results of this step can be
found in our replication package~\cite{brandt2020chunk-replication}.
Note that for most questions we allowed assigning multiple values, e.g.
if
two kinds of informations were targeted during a build log analysis.

\subsection{Results}
In the following, we will present the results of our literature survey.
Starting with the information that was targeted and what it was employed
for, over the techniques used until the origin of the build logs
which were
analyzed.

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/techniques.pdf}
		\caption{Frequency of different technique labels for
		labels $>1$ occurence.}
		\label{fig:litsur:techniques}
\end{figure}

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/info_target.pdf}
		\caption{Frequency of different targeted information
		labels for
		labels $>1$ occurence.}
		\label{fig:litsur:info_target}
\end{figure}

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/use.pdf}
		\caption{Frequency of different usage of output labels for
		labels $>1$ occurence.}
		\label{fig:litsur:use}
\end{figure}

\begin{figure}[tbp]
		\centering
		\includegraphics[width=\columnwidth,
		clip]{img/lit-sur/log_producer.pdf}
		\caption{Frequency of different log producer labels for
		labels $>1$ occurence.}
		\label{fig:litsur:log_producer}
\end{figure}

\subsubsection{Retrieved Information}
The information that was targeted is presented in
\Cref{fig:litsur:info_target} varied from article to article.
Most prominent was the search for errors (39\%) that occured within
the build process, followed by extracting the executed or the failing
tests
(both 11\%).

In most cases (51\%), a chunk was retrieved from the log, whereas 36\%
of the articles classified the articles into categories.
Other types of processing (e.g.
counting lines, summarization) were only
done in one case each.

The majority of articles (46\%) used the outcome of their build log
analysis
for research purpopses, as shown in \Cref{fig:litsur:use}.
Further uses were giving feedback to developers (10\%) or automatic
on-ward
processing of the retrieved information (8\%).

\subsubsection{Retrieval Technique}
\Cref{fig:lisur:techniques} presents the techniques which the articles
described for processing build logs.
43 of the 61 articles we inspected touched on how they are analyzing build
logs.
However, only 16 of these described their method in detail.

The most mentioned method (34\%) was using a parser, where we also
included
rather unprecise statements like ``we parse the build logs''.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning techniques such as natural language
processing or information retrieval techniques.

25\% of the articles claimed their implementation is available, however we
saw very low reuse of build log analysis tools within our survey.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent}, two used the
\emph{Maven Log Analyzer}, % TODO: cite
another two the \emph{MAKAO} tool.
% TODO: cite

\subsubsection{Build Logs}
Of the articles we surveyed, 30\% analyzed build logs produced by
Maven~\cite{maven2019website}, 16\% ones produced by Gradle % TODO: cite
and 10\% logs produced by Ant.
% TODO: cite
The distribution of supported build tools is shown in
\Cref{fig:litsur:log_producer}.
Only 7\% of the proposed methods claimed to be language-agnostic, while
several described they are covering multiple source build tools.
The majority of articles (42\%) targeted logs from a source which was not
targeted by any second article.

The main platform that build logs were collected from is Travis
CI, % TODO cite.
which was used in 38\% of cases.
18\% of the articles processed logs from TravisTorrent and 8\% included
build logs from industrial projects.

The number of logs analyzed varied greatly and we were not always able to
extract it confidently.
Articles reported processing from two up to 122 million logs.

31\% of the surveyed articles claimed to have published their data to
enable further research.
